Trail Saving on Backtrack

### 2020-03-02 figures/cactus_maple_new.tex
used maple data more consistent with definitions
a little cleaner

\addplot[red,mark=x] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_data.csv};
\addplot[green,mark=o] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_chrono_data.csv};
\addplot[blue,mark=+] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_trail_noforce_data.csv};
\addplot[cyan,mark=square] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_trail_noforce_1lvl_data.csv};
\addplot[gray,mark=triangle] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_trail_1lvl_5lbdreason_data.csv};

>>>>

\addplot[red,mark=x] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_data.csv};
\addplot[green,mark=o] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_chrono_data.csv};
\addplot[blue,mark=+] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_trail_noforce_data.csv};
\addplot[cyan,mark=square] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_trail_noforce_1lvl_again__data.csv};
%\addplot[gray,mark=triangle] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_trail_1lvl_5lbdreason_data.csv};
\addplot[gray,mark=triangle] table [x=index, y=original_time, col sep=comma] {results_maplelcmdist_trail_noforce_1lvl_again__5lbdreasons_data.csv};

### 2020-03-02 paper.tex
a little cleaner

\begin{figure}
\centering
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total & SAT & UNSAT & Avg. Par-2 \\ \hline
      maple           & 458          & 259 &  199  & 4746                             \\ \hline
      maple-chrono   & 470          & 271 &  199  & 4613                             \\ \hline
      maple-trail    & \textbf{472}          & 271 &  \textbf{201}  & 4618                \\ \hline
      maple-trail-multipleBT-lookahead & 471 & 272 &  199  & \textbf{4597}        \\ \hline
      maple-trail-multipleBT-lookahead-reason & 467 & \textbf{273} & 194 & 4668 \\ \hline
    \end{tabular}
    \caption{Table of results for MapleLCMDist.}
    \label{fig:maple}
\end{figure}

>>>>

\begin{figure}
\centering
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total & SAT & UNSAT & Avg. Par-2 \\ \hline
      maple           & 458          & 259 &  199  & 4746                             \\ \hline
      maple-chrono   & 470          & 271 &  199  & 4613                             \\ \hline
      maple-trail    & \textbf{472}          & 271 &  \textbf{201}  & 4618                \\ \hline
      maple-trail-multipleBT-lookahead & 471 & \textbf{272} &  199  & \textbf{4597}        \\ \hline
      maple-trail-multipleBT-lookahead-reason & 469 & 271 & 198 & 4633 \\ \hline
    \end{tabular}
    \caption{Table of results for MapleLCMDist.}
    \label{fig:maple}
\end{figure}
